Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-09 Paperfolder/Paperfolder.Rmd
updated discussion started

Our aim was to overcome these potential pitfalls, avoid misunderstanding, and provide a more straightforward answer to the main research question that whether someone answered he/she drank milk at the baseline of study had lower hazard of dying from stroke compared with his/her counterparts who said they never consumed milk. If the answer to the primary objective was yes, then the probabilities that individuals with different frequencies of milk intake may had lower hazard compared with those who never drank milk were calculated through a Markov Chain Monte Carlo (MCMC) simulation process. A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay or slow down the speed towards a stroke event from happening after controlling for the other potential confounders.

@@

In the JACC study cohort, we observed that

-

>>>>

Our aim was to overcome these potential pitfalls, avoid misunderstanding, and provide a more straightforward answer to the main research question that whether someone answered he/she drank milk at the baseline of study had lower hazard of dying from stroke compared with his/her counterparts who said they never consumed milk. If the answer to the primary objective was yes, then the probabilities that individuals with different frequencies of milk intake may had lower hazard compared with those who never drank milk were calculated through a Markov Chain Monte Carlo (MCMC) simulation process. A Bayesian survival analysis method was applied on an existing database and through which, we also provided estimates about whether drinking milk could delay or slow down the speed towards a mortality from stroke event from happening after controlling for the other potential confounders.

@@

In the JACC study cohort, our analysis showed that men in Japan who consumed milk almost daily had lower hazard of dying from stroke especially from cerebral infarction. Our evidence also suggested that stroke events were found to be delayed from happening among Japanese male daily milk consumers compared with non-consumers.

<!-- - comparison with previous meta-analysis -->
These findings are in line with our previous report [@wang_milk_2015] with further additional and more forthright evidence about whether and how certain we could hold about daily consumption of milk is contributing to a postponed stroke (mostly cerebral infarction) mortality event. A recent meta-analysis of 18 prospective cohort studies had shown a similar negative association [@DeGoede2016] between milk consumption and risk of stroke.
<!-- - potential biological reasons -->

<!-- - strength and limitation of current study -->

### 2020-07-09 Paperfolder/Paperfolder.tex
updated discussion started

In the JACC study cohort, we observed that

\begin{itemize}
\tightlist
\item
\end{itemize}

>>>>

In the JACC study cohort, our analysis showed that men in Japan who
consumed milk almost daily had lower hazard of dying from stroke
especially from cerebral infarction. Our evidence also suggested that
stroke events were found to be delayed from happening among Japanese
male daily milk consumers compared with non-consumers.

These findings are in line with our previous report
\citep{wang_milk_2015} with further additional and more forthright
evidence about whether and how certain we could hold about daily
consumption of milk is contributing to a postponed stroke (mostly
cerebral infarction) mortality event. A recent meta-analysis of 18
prospective cohort studies had shown a similar negative association
\citep{DeGoede2016} between milk consumption and risk of stroke.
